% Mengubah keterangan `Abstract` ke bahasa indonesia.
% Hapus bagian ini untuk mengembalikan ke format awal.
\renewcommand\abstractname{Abstrak}

\begin{abstract}

  % Ubah paragraf berikut sesuai dengan abstrak dari penelitian.
  \emph{Face detection algorithms nowadays have developed rapidly. 
  This is inseparable from the need for face detection algorithms as an authentication tool and biometric-based security system. 
  However, the main problem of the face detection algorithm is the accuracy that could vary according to environmental conditions. 
  In this final project, we analyze performance of face detection algorithm based on pyramid feature 
  in the surveillance environment. 
  The analysis was carried out with CCTV video as input for the face detection 
  algorithm and carried out with several different scenarios. 
  Some of the scenarios carried out are light conditions, 
  movement of people, multiple face detection, and face detection in disguise. 
  In this research, the latest face detection method based on feature pyramid is used. 
  The main metric used to evaluate the face detection algorithm method based on feature pyramid is 
  mean average precision (mAP) by comparing manual labeling conditions and labeling conditions obtained 
  from the face detection system. 
  In terms of processing time, 
  frame rate per second (FPS) will be used for evaluation under different hardware configuration conditions. 
  The results show that the mobilenet0.25 backbone in the feature pyramid-based face detection system excels in processing time 
  and FPS parameters in all scenarios that are run, while the resnet50 backbone excels in accuracy parameters (mAP) in scenarios where the mobilenet0.25 backbone is difficult to perform detection.}

\end{abstract}

% Mengubah keterangan `Index terms` ke bahasa indonesia.
% Hapus bagian ini untuk mengembalikan ke format awal.
% \renewcommand\IEEEkeywordsname{Kata kunci}

\begin{IEEEkeywords}

  % Ubah kata-kata berikut sesuai dengan kata kunci dari penelitian.
  System Performance Evaluation, Face Detection System, Feature Pyramid Network

\end{IEEEkeywords}
